\chapter{Introduction}
\label{ch:intro}

\begin{gram}
\label{ch:intro::preamble}

This small book contains miscellaneous information for Fall 2020 hybrid teaching.  
%
Specifically,
\begin{itemize}
\item
\href
{ch:equipment}
{this chapter on audio-visual equipment and accessories} contains information about basic remote teaching equipment  that the faculty can purchase on their own and be reimbursed,
%

\item
\href
{ch:displays}
{this chapter on Pen Displays} contains information about a pen display that you can request for your teaching.
\end{itemize}
%
\end{gram}

\begin{gram}[General Purchasing Instructions]
\label{ch:intro::purchase}
For each purchase please follow the instructions at the top of the
page (chapter).

%
Please note that 
\begin{itemize}
\item 
Only the equipment listed on this book is approved for reimbursement.
For other purchases, the faculty are expected to use their own funds.

\item 
The equipment is reimbursable only if you are teaching in Fall 2020.

\end{itemize}
%
\end{gram}

\begin{important}[Got Questions?]
If you have questions related to this material, e.g.,  about a piece of equipment, or purchasing instructions, please use the Diderot platform that hosts this page to ask your question.   
%
Please create a Diderot account  with a *andrew.cmu.edu* email address and enter (click)  the course (15001 Hybrid Teaching).  You can use the code that was separately emailed to you to enter the class. 
%
Diderot supports integrated discussions.  Press on any “mail” icon under a paragraph and create your question about that paragraph.  You can create general questions in the post office (click the Mail icon on the toolbar).
\end{important}

\begin{gram}[Request for Contributions]
\label{ch:intro::contribute}
This information is public and created by our community for our community.  Contributions based on your knowledge and experience are highly appreciated and would help other faculty members and our community in these unprecedented times.  
%
Please consider contributing and volunteering some of your time.
%
You can find the (LaTeX) sources for this book in the following 
\href
{https://github.com/diderot-edu/fall2020}
{github repository}.
\end{gram}
