\chapter{ Equipment for Teaching Assistants}

\begin{preamble}
Mobile phones have good cameras and microphones that can compete with
some of the best webcams and USB microphones out there.
%
Furthermore, they can be connected to a zoom call as a second camera
%
(e.g., 
\href
{grm:tas::mobile-cam-as-doccam}
{as a document camera}
).
%
Your teaching assistants can therefore create recitations recordings and hold office hours (e.g., by using their phone as a document camera) by using their mobile phones and several simple pieces of equipment.
%
Here we list the equipment that you can purchase for your TAs for this purpose.
\end{preamble}

\begin{gram}[Supplies for Teaching Assistants]
We recommend each instructor to supply their TAs with some
remote-teaching equipment that can be used for recording recitation
videos and holding office hours.
%
It is not difficult to imagine a whole range of equipment for this
purpose; our purpose here is to be resourceful and to focus on the most
effective pieces of equipment.
%

\textbf{Budget:}

As an instructor, you can purchase (and be reimbursed for)
\begin{itemize}
\item one whiteboard for each of your TAs (undergraduate and graduate), who will hold office hours or deliver recitations;


\item one board marker and eraser set for each TA (undergraduate and graduate);

\item
up to two tripods per class if these will be used for producing lecture/recitation/practice videos;

\item we will not reimburse shipping charges but you can avoid these by  purchasing multiple units at once and distributing the units yourself or asking your TAs to do so.

\end{itemize}

\end{gram}

\begin{important}[Reimbursement]
Simply make the purchase by following the stated guidelines and ask
your administrative assistant for reimbursement (your assistant will
contact Jessica Packer).
%
Because these purchases are relatively small, please do not send unnecessary inquiries, e.g., about alternative equipment.
%
In principle, only the equipment listed here at the listed prices will
be reimbursed, but depending on your needs you may purchase, smaller
or different whiteboards, different set of markers, etc.,  as long as the
total cost remains the same or less.
\end{important}


\begin{gram}[Using your Mobile Phone as a Document Camera]
\label{grm:tas::mobile-cam-as-doccam}
Sam Westrick demonstrates how to use a mobile phone as a document camera in a zoom call. 
%
\video
{https://www.youtube.com/embed/B--lh043b9Y}
{Using your Mobile Phone as a Document Camera}
\end{gram}

\section{Whiteboards and Markers}

\begin{gram}[Whiteboards]

During remote lectures, the students prefer to see more than just the
face of their instructors.
%
As an instructor or a TA, you might want to use a small portable
whiteboard in your recitations and office hours along with a camera
and microphone that can capture the board along with you. 
%
We recommend using a small 3 feet by 2 feet whiteboard.  
%

\textbf{Where to buy:}

\begin{itemize}
\item
3 x 2 whiteboard on

\href{https://www.walmart.com/ip/Universal-Melamine-Dry-Erase-Board-36-x-24-Satin-Finished-Aluminum-Frame/21794195?wmlspartner=wlpa&selectedSellerId=1194&&adid=22222222227015737388&wl0=&wl1=g&wl2=c&wl3=52438033391&wl4=pla-83993817911&wl5=1025202&wl6=&wl7=&wl8=&wl9=pla&wl10=112550058&wl11=online&wl12=21794195&veh=sem&gclid=Cj0KCQjwhIP6BRCMARIsALu9Lfmsq_QIRmgF0rbJxUlILrtcELAuduVKI6z9GdzLxIafjLXdwYfXkmMaAoogEALw_wcB}
{Walmart for \$20}

\item
3 x 2 whiteboard on

\href{https://www.zoro.com/zoro-select-dry-erase-board-36-w-silver-1nup9/i/G1291367/}{Zoro for \$24}



\item Note: similar whiteboards are available on Amazon and other online shops with free-shipping but the prices are higher.  Please avoid paying more; instead batch your purchase as needed to avoid shipping charges.
%% \item 
%% \href{https://www.shoplet.com/Universal-Adjustable-White-Board-Easel/UNV43033/spdv?pt=rk_frg_pla&gclid=Cj0KCQjwvvj5BRDkARIsAGD9vlIAZ8S65M9rY3gJkgpDk6kzZXPSJ-ljV9qVFojSsax5k88zKntEyP0aAuOHEALw_wcB}
%% {Whiteboard and stand for \$75 (free shipping)}

%% \item
%% \href{https://www.officesupply.com/office-supplies/boards-easels/boards/easel-boards/universal-erase-easel-board-easel-height-board-white-silver/p192673.html?ref=pla&utm_source=google&utm_medium=cpc&adpos=&scid=scplp192673&sc_intid=192673&gclid=Cj0KCQjwhIP6BRCMARIsALu9LfmKVfLex71VAT_aU8G5FnQ7ULqQ4m__EUZgIeTURj1PjGfqEOdedvcaAux8EALw_wcB}
%% {Whiteboard and stand for \$75 (free shipping)}

\end{itemize}

\end{gram}


\begin{gram}[Markers and Erasers]
For remote teaching using a whiteboard, we recommend chisel tip or thick tip markers. If you are working on a desk with an overhead camera you could use thinner ones.

\textbf{Where to buy:}

Available on
\href{https://www.amazon.com/80556-Low-Odor-Chisel-Assorted-7-Piece/dp/B00006JNJP/ref=sr_1_29?crid=3BOQYY0J0U2OZ&dchild=1&keywords=whiteboard+markers&qid=1598114240&refinements=p_n_location_browse-bin%3A6473192011&rnid=2726075011&s=office-products&sprefix=whiteboard%2Caps%2C162&sr=1-29}
{Amazon.}

\end{gram}

\section{Tripods}

We recommend all TAs to purchase a tripod stand. This would allow them to use their mobile phones for recording lectures and as a document camera.  
%
Because these items are reusable, we expect each TA to purchase their own.
%
But if your TAs are teaching recitations and you expect them to
produce lecture recordings, you can purchase up to two of these
tripods listed below for your TAs.
%

\begin{gram}[Extendable Tripod]
An extendable tripod works well for doing lecture recordings in front of a small whiteboard.

\textbf{Where to buy:}

Available
\href{https://www.amazon.com/UBeesize-Extendable-Bluetooth-Aluminum-Lightweight/dp/B07NWC3L95/ref=pd_ybh_a_27?_encoding=UTF8&psc=1&refRID=7G79BF5K1T32C0NJXB51}
{on Amazon for \$26}
\end{gram}

\begin{gram}[Flexible desktop Tripod]

This is a flexible tripod that can be used in many different
configurations.  Note that it is short and is not extendable. 


\textbf{Where to buy:}

Available on 
\href
{https://www.amazon.com/gp/product/B07837W5NX/ref=ppx_yo_dt_b_search_asin_title?ie=UTF8&psc=1}
{Amazon for \$20}
\end{gram}

\begin{gram}[Mama-Win]
\label{grm:tas::tripod::mamawin::main}

\textbf{Overview}

This is a light weight mini webcam tripod for smartphone and Logitech webcam.

%
\begin{itemize}
\item
Mini tripod with adjustable-height metal legs and rubber feet

\item
Compatible with small digital cameras (not DSLRs), GoPro devices, and smartphone adapters 

\item
Mini ball head for 360-degree rotation and 90-degree tilt

\item
Provides Support And Stability For Cameras, Webcams, Imaging Devices, etc

\end{itemize}



\textbf{Expected price}

\$13

\textbf{Where to buy:}

Available on
\href{https://www.amazon.com/Lightweight-Webcam-Tripod-Logitech-Camera/dp/B076SHC6RN/ref=sr_1_1_sspa?crid=2T6CQ3HNRR1XR&keywords=logitech+c920&qid=1582900721&s=electronics&sprefix=logitech+c,electronics,172&sr=1-1-spons&psc=1&spLa=ZW5jcnlwdGVkUXVhbGlmaWVyPUE1VjVUUFpKTU83QUkmZW5jcnlwdGVkSWQ9QTA1NTk1OTVLT1IyTzdRRFVEWkImZW5jcnlwdGVkQWRJZD1BMDEyNzk2NzEyTDVSOEdSQ1QxTEgmd2lkZ2V0TmFtZT1zcF9hdGYmYWN0aW9uPWNsaWNrUmVkaXJlY3QmZG9Ob3RMb2dDbGljaz10cnVl}{Amazon}

\end{gram}

