\chapter{Basic Equipment}
\label{ch:equipment}

\begin{gram}[Equipment Checklist]
\label{grm:equipment::checklist}
	\begin{enumerate}
		\item Stable, high-speed internet connection (wired ethernet highly recommended). See \href{sec:equipment::internet}{Internet}
		\item Good microphone with clean sound, low echo, and low background noise. See \href{sec:equipment::mics}{Microphones}
		\item Good webcam setup so you are well framed, well lit, and comfortable. See \href{sec:equipment::web-cam}{Webcams}
	\end{enumerate}
\end{gram}

\begin{important}[Supply Issues]
Equipment supplies, especially for Webcams, is currently in flux, with many cameras selling out. 
%
If you don't need a piece of equipment immediately, we recommend trying to backorder to be notified when it becomes available.  
%
Best place to do this is probably on the producer's website.
%
For example, on Logitech web site, you may backorder equipment such as
cameras and they will let you know when they can fill these orders.
%
If you need the piece of equipment sooner, then there we recommend
purchasing of of the ``no-name'' equivalents.  
%
Information on some no-name alternatives are provided below.
\end{important}


\begin{gram}[Purchasing Instructions]
\label{grm:equipment::preamble}
We have compiled a list of approved and recommended basic audio and video
equipment for teaching.
%
We encourage you to purchase one camera, one microphone, and the accessories (tripods, adapters, etc) either on your own (and request reimbursement through your administrative assistant) or through your administrative assistant (on their procurement card). Please tell your admin that this purchase is to be charged to the ``Fall 2020 Remote Equipment SCS'' string. 

As a reminder
\href{ch:intro::purchase}{please note the conditions for reimbursements}.
%
If you are purchasing yourself, then please make sure that the price
that you are paying matches the expected prices that is included in
the description of
%
These and similar equipment are under high demand and some companies
such as Amazon apply the so called ``dynamic pricing'' that can change
the price of an item quite significantly.
%
We have included a number of direct links to online stores that you can make a purchase but there are many other sellers. 


We hope that the information included here can help you make an informed decision about your equipment needs.
%% %
%% If you would like to compare the equipment yourself, we have a limited number of loaners that you can try out.  
%
If you have questions are would like to discuss, then please create a
question by clicking the mail icon at the bottom right of the relevant
paragraph or going to the ``Post Office'' above (these features are
available after you log on to Diderot).

\end{gram}

\section{Stable internet}
\label{sec:equipment::internet}

\begin{gram}[Wiring Up]
\textbf{We highly recommend that you use a wired ethernet connection directly from you router to your computer.
%
WiFi connections are inherently unstable due to many reasons, including interference from other WiFi users, which is very difficult to control.
}

Having a stable and high-speed internet connection is critical for communicating effectively with your class. 
If your connection is weak, your video or audio will drop out and your students will not hear or see you.
This often happens without you knowing it or only receiving a Zoom ``unstable internet connection'' warning.


A Cat6 ethernet cable will work fine and can be found in lengths up to 150 ft (45 m) and in a variety of colors to mach your home d\'{e}cor :)

\textbf{Expected Price}
\begin{itemize}
	\item 3 ft - \$6
	\item 10 ft - \$7
	\item 25 ft - \$10
	\item 50 ft - \$20
	\item 100 ft - \$22
	\item 150 ft - \$32
\end{itemize}

\textbf{Where to buy}
\begin{itemize}
\item \href{https://www.amazon.com/AmazonBasics-RJ45-Cat-6-Ethernet-Patch-Cable-10-Feet-3-Meters/dp/B0134QJH4G/ref=sr_1_5?dchild=1&keywords=cat6%2Bethernet%2Bcable&qid=1597264670&sr=8-5&th=1}{Amazon 3 - 50 ft}
%
\item \href{https://www.amazon.com/Cable-Matters-Snagless-Ethernet-Black/dp/B007NZGPAY/ref=sr_1_3?dchild=1&keywords=cat6%2Bethernet%2Bcable&qid=1597264670&sr=8-3&th=1}{Amazon 20 - 150 ft}
\end{itemize}
\end{gram}


\begin{note}
	Check your internet using \href{https://www.speedtest.net}{Speedtest.net} or \href{https://www.nperf.com/en/}{nperf.com}. 
	Zoom requires at least 2 Mbps upload and 4 Mpbs download (with dual screen) \href{https://support.zoom.us/hc/en-us/articles/204003179-System-Requirements-for-Zoom-Rooms}{Zoom Requirements} 
	but you will want to see much higher numbers and low fluctuations during the test. If you are on WiFi run the test next to your router 
	and then in another room to see the difference.
\end{note}


\begin{note}
If your computer does not have an ethernet (RJ45) port you will need to get an adapter.
If you have a Mac or PC with USB-C ports, get a USB-C to Ethernet adapter or USB-C multiport hub (make sure it has ethernet!).

\begin{itemize}
	\item \href{https://www.amazon.com/Adapter-Charging-Ethernet-Compatible-Thunderbolt/dp/B07TVSLDND/ref=sr_1_3?dchild=1&keywords=usb+c+hub+with+ethernet&qid=1597265719&refinements=p_72%3A2661618011&rnid=2661617011&sr=8-3}{USB-C Hub with Ethernet}
	\item \href{https://www.amazon.com/Anker-Ethernet-Portable-1-Gigabit-Chromebook/dp/B00ZZ6NW5E/ref=sr_1_5?dchild=1&keywords=usb+c+to+ethernet&qid=1597265911&sr=8-5}{USB-C to Ethernet only}
\end{itemize}


If you have a PC with USB-3 ports, get a USB-3 to Ethernet adapter.
\begin{itemize}
	\item \href{https://www.amazon.com/AmazonBasics-1000-Gigabit-Ethernet-Adapter/dp/B00M77HMU0/ref=sr_1_4?dchild=1&keywords=usb+3+to+ethernet&qid=1597266009&sr=8-4}{USB-3 to Ethernet only}
\end{itemize}

\end{note}

\section{Microphone}
\label{sec:equipment::mics}

\begin{gram}[How to choose a Mic?]
\label{grm:equipment::mics::how}
Having a good microphone is extremely important for remote teaching. 
%
If the camera quality is a bit off, your audience  can often adjust.
%
But poor audio quality is usually a deal breaker.
%
Therefore, it is important to pick the right microphone and learn how to use it. 
%
Perhaps, the most important consideration is whether you want to have a
omni-directional or a more focused (unidirectional) microphone.
%
For our purposes here we will consider cardioid focused
microphones, which pick up the voice from the front and a bit from the
side, but very little from the back.  This allows you to move around a
bit but it does not pick up extra noise from the surrounding.
%
Here are some scenarios for picking a mic:

\begin{itemize}
	\item I am in a quiet room with low echo and little background noise - if you have a Mac the built in mic is probably ok. If you have a PC or want better audio, consider the Fifine.
	\item I like to stand up and move around when I present - get a lapel mic like the Samson.
	\item I want to have the richest sounding voice possible (like my favorite podcaster) and do not move around when I present - get the Blue Yeti, Snowball or Fifine.
	\item I want to move around, wear over the ear headphones, or like looking like I am on the Mission Control team - consider a head ModMic or a wireless headset mic.
\end{itemize}
\end{gram}

\begin{gram}[Comparison between various Microphones]
\label{grm:equipment::mics::comparison}
Here is a sample video that Nikolas Martelaro over in the HCII made showing the differences between microphones when streaming with Zoom. In the video he tests a lavalier mic, the built-in mics on his MacBook Pro and Logitech webcam, and a high-quality cardioid mic.

\video{https://www.youtube.com/embed/iNwQN0R6pSs}{Microphone Comparison}
\end{gram}

\subsection{Blue Snowball iCE Mic}
\label{sec:equipment::bluesnow}

\begin{gram}
\label{grm:equipment::bluesnow::overview}

\textbf{Overview}

This is an Omnidirectional Microphone. If you plan to move around the
space, e.g., between a chalk/marker board, screen, an omnidirectional
microphone like the Blue Snowball or a lapel microphone are good
options.
%
The disadvantage of this microphone is that it will pick up noise from the surrounding space.
%
If you don't have a quiet office (e.g., expect dogs barking, traffic noise, etc), then this microphone is not the best choice.  
%
You might want to choose a lapel microphone or something more directional.




\textbf{More Details}

For full details, see \href{https://www.bluedesigns.com/products/snowball-ice/}{Blue Designs web site}.

\begin{itemize}
\item
Compatible with PC and Mac.

\item  USB 2.0 device (USB 3.0 compatible as per USB 3.0 backward compatibility specification)

\item Custom condenser capsule offers crystal clear audio

\item Record vocals, create podcasts, and add narration to your home movies

\item Frequency Response: 40 –18 kHz

\item Easy plug and play directly to your Mac or PC—no drivers to install
\end{itemize}



\textbf{Expected price}

\$50


\textbf{Where to buy}


\begin{itemize}
\item 
\href{https://www.bluedesigns.com/products/snowball-ice/}{Blue Designs}

\item 
\href{https://www.amazon.com/Blue-Snowball-Condenser-Microphone-Cardioid/dp/B006DIA77E/ref=sxin_2_ac_d_rm?ac_md=1-1-c25vd2JhbGwgbWljcm9waG9uZQ%3D%3D-ac_d_rm&crid=35T8W1KNGCU61&cv_ct_cx=blue+yeti+usb+microphone&keywords=blue+yeti+usb+microphone&pd_rd_i=B006DIA77E&pd_rd_r=3aa58f9d-30b3-4a94-a0f9-899d4ec51554&pd_rd_w=TANss&pd_rd_wg=OOiJB&pf_rd_p=ec111f65-4a46-499c-be78-f47997212bd0&pf_rd_r=BKY12JJMDCSM54ABWTDX&psc=1&qid=1582900292&sprefix=Blue+ye,aps,168}{Amazon}
\end{itemize}

\end{gram}

\begin{gram}[Fifine versus Blue Snowball]
\video{https://www.youtube.com/embed/YvM_S1nZjb4}{Fifine versus Blue Snowball}
\end{gram}

\begin{gram}[Comparison between Blue Snowball versus Blue Yeti]
\video{https://www.youtube.com/embed/ZufYPL0XcVk}{Blue Snowball versus Blue Yeti}
\end{gram}

\subsection{Samson Lapel Mic}
\label{sec:equipment::samsonlapel}

\begin{gram}
\label{grm:equipment::samsonlapel::main}

\textbf{Overview}

If you expect to have noise from the surrounding when you are teaching
(your office receives traffic noise, there are multiple people sharing
the same office space, etc), then you will want to have a
directional microphone.  
%
In our tests, we have found that a lapel microphone is best for this purpose. A lapel mic or a wireless headset mic is also a good choice if you like to move around while you present, for example while working on a whiteboard.
%


\textbf{More Details}

\href{http://www.samsontech.com/samson/products/wireless-systems/xpd-series/xpd2lav/}
{Samson XPD2 Lavalier USB Digital Wireless System (SWXPD2BLM8)}

\begin{itemize}
\item 2.4GHz USB digital wireless system
\item Plug-and-play operation with Mac and Windows computers. 
\item Works with iPads and iPhones via Apple's Lightning to USB camera adapter and Android devices via a host OTG Adapter.

\item RXD2 USB receiver with 1/8" (3. 5mm) headphone/ line output that allows for headphone monitoring or connection to any mixer
\item PXD1 belt pack Transmitter offers 20 hours of battery life using two AA batteries (not included)
\item Includes Samson LM8 omnidirectional lavalier microphone
\item 100' Operating range (line of sight)
\item System includes lapel clip and USB extension cable
\end{itemize}

\textbf{Expected price}

\$120

\textbf{Where to buy}

\begin{itemize}

\item \href{https://www.amazon.com/Samson-Wireless-Microphone-System-SWXPD2BLM8/dp/B07HPRZBKC/ref=sr_1_6?crid=3V47B7B3X9SJ5&keywords=wireless+usb+lapel+microphone&qid=1582899680&sprefix=Wireless+USB+lapel+,aps,143&sr=8-6}{Amazon}

\item 
\href{https://www.bhphotovideo.com/c/product/1440151-REG/samson_swxpd2blm8_xpd2_lavalier_usb_wireless.html/?ap=y&ap=y&smp=y&smp=y&lsft=BI%3A514&gclid=EAIaIQobChMIiIOHy-_06QIVUopaBR150wxWEAQYASABEgJL5vD_BwE}{B\&H Photo}
\end{itemize}
\end{gram}

\subsection{ModMic}
\label{sec:equipment::modmic}

\begin{gram}
\textbf{Overview}
Another option for focused audio is to use a headset mic. Headset mics put the microphone right near your mouth.
This allows you to reduce the gain and prevent picking up background noise.
Typically, headset mics result in high quality audio capture but have a few downsides.
\begin{itemize}
\item The gain must be tuned so that your voice does not ``clip'' and cause the audio to become very loud and noisy. 
\item the mic should be position far enough away so that you avoid ``popping.'' This is that breathy and loud sound you hear when you say `P's' and the audio pops. This can usually be avoided by placing the mic about 1 - 2 inches (25 - 50 mm) from the \textit{corner} of your mouth.
\item Some people do not like the look of a mic across their face. Some people do not mind and kinda like the NASA control room look.
\end{itemize}

If you like using over the ear headphones, you can purchase headphones with built in headset mics. These are often found in gaming headsets.

If you already have headphones that you like and would like to add a headset mic, the ModMic is a nice option. 

The ModMic comes in different configurations including wireless Bluetooth, USB, and analog (3.5mm). The ModMic has a magnet that let's you quickly attach the mic to the side of your over-the-ear headphones.

More information and their online store is here: \href{https://antlionaudio.com/collections/microphones}{ModMic}

Here is a video showing a 
\video{https://www.youtube.com/embed/MgXA0uZ15zE}
{comparison of the different ModMics}

\textbf{Expected Price}
\begin{itemize}
	\item \href{https://antlionaudio.com/collections/microphones/products/modmic-wireless}{ModMic Wireless} \$120 (recommended)
	\item \href{https://antlionaudio.com/collections/microphones/products/modmic-usb}{ModMic USB} \$80 (recommended)
	\item \href{https://antlionaudio.com/products/modmic-uni-usb-sound-card}{ModMic Analog and USB Sound card} \$55 (Recommended if you have a set of analog headphones you already like) 
	\item \href{https://antlionaudio.com/collections/microphones/products/modmic-uni}{ModMic Analog} \$50 (note: you need an analog mic input on your computer or a headphone and mic splitter for a combo audio jack - the kind on Mac's and many lighter PC's with a single audio output) 
\end{itemize}

\textbf{Where to buy}
Note: Stocks may be low at different vendors. Here are some options.

\begin{itemize}
	\item \href{https://antlionaudio.com/collections/microphones}{ModMic} (Direct purchase from manufacturer)
	\item \href{https://www.bhphotovideo.com/c/search?Ntt=modmic&N=0&InitialSearch=yes&sts=ma}{B\& H}
	\item \href{https://www.amazon.com/s?k=modmic&ref=nb_sb_noss_1}{Amazon}
\end{itemize}

\end{gram}

\subsection{Fifine K670}
\label{sec:equipment::fifine}

\begin{gram}
\label{grm:equipment::fifine::main}
If you don't want to use a Lapel Microphone and you have a relatively
noisy office, then you want to consider a focused Microphone.
Fifine K670 is a focused (cardioid) USB 2.0 microphone that
delivers very good quality overall sound.

\textbf{More Details}

\begin{itemize}
\item
This is all metal construction has a very solid feel to it.
\item
It has quite a long cable (perhaps 6 feet) that can be wrapped around its stand when not needed.
\item 
It is not big and bulky.
\item
More details are on \href{https://fifinemicrophone.com/products/usb-microphone-for-mac-and-windows-k670}{Fifine web site}
\end{itemize}

\textbf{Expected Price}

\$ 55

\textbf{Where to buy}

\begin{itemize}
\item 
\href{https://www.amazon.com/Microphone-FIFINE-Computers-Podcasting-K670/dp/B079HRFH2Y/ref=asc_df_B079HRFH2Y/?tag=hyprod-20&linkCode=df0&hvadid=380013417597&hvpos=&hvnetw=g&hvrand=6999453823816156640&hvpone=&hvptwo=&hvqmt=&hvdev=c&hvdvcmdl=&hvlocint=&hvlocphy=1025202&hvtargid=pla-878206170477&psc=1&language=en_US&tag=&ref=&adgrpid=77922879259&hvpone=&hvptwo=&hvadid=380013417597&hvpos=&hvnetw=g&hvrand=6999453823816156640&hvqmt=&hvdev=c&hvdvcmdl=&hvlocint=&hvlocphy=1025202&hvtargid=pla-878206170477}{Amazon}
\item \href{https://fifinemicrophone.com/products/usb-microphone-for-mac-and-windows-k670}{Fifine}
\end{itemize}
\end{gram}

\subsection{Blue Yeti}
\label{sec:equipment::blueyeti}

\begin{gram}
\label{grm:equipment::blueyeti::main}
%
Blue Yeti as multi-dimensional microphone.
%
It is optimized for focused (cardioid) use like the Fifine K670
but it also allow you to broaden directionality to includes the sides
and the back, moving towards an omnidirectional microphone.
%
It does not do a good job, however, with the omnidirectional use, and we don't recommend this microphone if you plan to move about a lot as you teach.
%
But if you are planning on being mostly stationary, this microphone is excellent and is considered to be the benchmark.
%
In practice and in uni-directional use the difference between this and
the Fifine K670 is small.  Fifine is also a bit simpler with fewer knobs to turn and thus fewer things to go wrong.  Blue yeti is quite a bit larger than Fifine.


\textbf{More Details}

\begin{itemize}
\item This is quite big and bulky for most uses. 
\item 
You can find full technical details here on \href{https://www.bluedesigns.com/products/yeti/}{Blue Designs}.
\end{itemize}

\textbf{Where to buy}

You expect to pay about 130 dollars for this microphone.  If you use Amazon to do your purchase, then you might find that the price is a lot higher, because of Amazon's dynamic pricing.  Please try other web sites such as 

\begin{itemize}
\item
\href{https://www.bhphotovideo.com/c/product/1252288-REG/blue_yeti_whiteout_yeti_usb_microphone_whiteout.html/?ap=y&ap=y&smp=y&smp=y&lsft=BI%3A514&gclid=CjwKCAjwgdX4BRB_EiwAg8O8HaL477lNngiVZfES7WLhUcJSUUvOZpExsDJj6nonuKow3CfyNGzRqRoC-dAQAvD_BwE}{B\&H Photo}
\item 
\href{https://www.dell.com/en-us/shop/blue-microphones-yeti-microphone-usb-aztec-copper/apd/aa829519?gacd=9614064-1012-5761040-0-0&dgc=st&gclid=CjwKCAjwgdX4BRB_EiwAg8O8HUjMAfBK6gO_-L-fdNSOjOlY2YqmqpLKR2qxP7hb-yRx8xlw1bscKBoCk0wQAvD_BwE&gclsrc=aw.ds}{Dell}
\end{itemize}
\end{gram}

\begin{gram}[Fifine versus Blue Yeti]
\video{https://www.youtube.com/embed/THnwsa32j_w}{Fifine versus Blue Yeti}
\end{gram}

\subsection{Blue Yeti Nano}
\label{sec:equipment::blueyetinano}

\begin{gram}
\label{grm:equipment::blueyetinano::main}
%
This is a small version of Blue Yeti microphone.
%
It has a focused (cardioid) and omnidirectional support.
%
It produces very good sound quality that is essentially the same as Blue Yeti.


\textbf{More Details}

You can find full technical details here on \href{https://www.bluedesigns.com/products/yeti-nano/}{Blue Designs: Yeti Nano}.


\textbf{Where to buy}

You expect to pay about 100 dollars for this microphone.  If you use Amazon to do your purchase, then you might find that the price is a lot higher, because of Amazon's dynamic pricing.  Please try other web sites such as 

\begin{itemize}
\item
\href{https://www.bhphotovideo.com/c/l-search?q=Blue%20Yeti%20Nano&N=0}{B\&H Photo}
\item 
\href{https://www.amazon.com/Blue-Yeti-Premium-Recording-Streaming/dp/B07DTTGZ7M}{Amazon}
\end{itemize}
\end{gram}

\begin{gram}[Blue Yeti versus Blue Yeti Nano]
\video{https://www.youtube.com/embed/sCR7FPP47As}{Blue Yeti versus Blue Yeti Nano}
\end{gram}

\section{Web Cam}
\label{sec:equipment::web-cam}

\begin{gram}[Features]
When selecting a webcam, try to look for the following features:

\begin{itemize}
	\item At least 720p resolution (1080p is better)
	\item h.264 encoding (this results in better video quality)
\end{itemize}
\end{gram}

\subsection{Logitech C920S HD Pro Webcam}
\label{sec:equipment::logitech-920}

\begin{gram}
\label{grm:equipment::logitech-920::main}
\textbf{Overview}

This is an HD Camera.  Full details are available on 
%
\href{https://www.logitech.com/en-us/product/hd-pro-webcam-c920s}{Logitech web site}.
%
\begin{itemize}
\item
Full HD 1080P video calls : Premium video quality.
\item
Full HD 1080P video recording : A glass lens and full HD mean your recorded videos are crisp and vibrantly colored
\item
HD auto-focus and light correction : Enjoy razor sharp high def in every environment

\item
Stereo audio with dual mics : Capture natural sound on calls and recorded videos. 

\item 
Platform compatibility skype, Google hangouts and FaceTime for Mac
Cable length: 5 feet (1.5 meters)
\end{itemize}


\textbf{Expected price}

\$69

\textbf{Where to buy}

\begin{itemize}
\item
\href{https://www.amazon.com/Logitech-Widescreen-Calling-Recording-Desktop/dp/B006JH8T3S/ref=sr_1_2?crid=2T6CQ3HNRR1XR&keywords=logitech+c920&qid=1582900645&s=electronics&sprefix=logitech+c,electronics,172&sr=1-2}{Amazon}
\item
\href{https://www.bhphotovideo.com/c/product/1461727-REG/logitech_960_001257_c920s_hd_pro_webcam.html}{B\&H Photo}
\item
\href{https://www.staples.com/logitech-c920s-pro-hd-webcam/product_24383955}{Staples (in-store only usually)}
% \item
% \href{https://www.amazon.com/Logitech-C920-Pro-Webcam-Black/dp/B00829D0GM/ref=sr_1_3?dchild=1&keywords=Logitech+C920+HD+Pro+Webcam&qid=1597029767&sr=8-3}{Amazon but for \$159 (thanks dynamic pricing...)}
\end{itemize}

This webcam is now largely unavailable or double the price because of demand during the
COVID-19 pandemic.

\textbf{Please do not buy if this camera is double the expected price (>\$140).}

We are evaluating the Logitech C930e series as an
option with very similar features, including HD video and integrated
microphones.
\end{gram}

\subsection{Logitech C930E}
\label{sec:equipment::logitech-930}
\begin{gram}
\label{grm:equipment::logitech-930::main}
Logitech C930E is the new version of Logitech C920S, which has been unavailable.

The technical details are similar.  You can read about it on
%
\href{https://www.logitech.com/en-us/product/c930e-webcam}{Logitech web site}.

\textbf{Expected price}

\$169

\textbf{Where to buy}

\begin{itemize}
\item
\href{https://www.amazon.com/Logitech-C930e-1080P-Video-Webcam/dp/B00CRJWW2G}{Amazon}.
\item 
\href{https://www.dell.com/en-ca/work/shop/logitech-c930e-hd-webcam/apd/a6880908/pc-accessories}{Dell}
\item
\href{https://www.bhphotovideo.com/c/product/977620-REG/logitech_960_000971_c930e_webcam_usb.html}{B\&H}
\end{itemize}

\end{gram}

\subsection{No-name HD Webcams}
\label{sec:equipment::no-name}

\begin{gram}[No-Name Webcams]
\label{grm:equipment::no-name::main}
If the above cameras are sold out, there are lots of no-name HD webcams available on Amazon. 
The key features to look for are:

\begin{itemize}
	\item HD 1080p resolution
	\item h264 encoding (note that this isn;t required but usualy results in better quality)
	\item Field of View - the Logitech has a $78^{\circ}$ FOV, narrower is good for sitting close, wider is better for standing and moving around or capturing a whiteboard.
\end{itemize}
%

\href{https://www.amazon.com/s?k=h264+webcam&ref=nb_sb_noss_2}{Amazon Search for h264 webcams}.

\textbf{Expected price}

\$35 - \$90

\textbf{Some options that might be in stock}

\begin{itemize}
\item
\href{https://www.amazon.com/Widescreen-Calling-Recording-Digital-Microphone/dp/B07925CYP5/ref=sr_1_7_sspa?dchild=1&keywords=h264+webcam&qid=1597071160&sr=8-7-spons&psc=1&smid=AWO8QGEAIYIUK&spLa=ZW5jcnlwdGVkUXVhbGlmaWVyPUExRVNTTjJZRURLNFE3JmVuY3J5cHRlZElkPUEwMjUzMDY0VzI3Nkw0RlVaQzg4JmVuY3J5cHRlZEFkSWQ9QTAyMDgyNzIyOUtNWjUwUVZEVktPJndpZGdldE5hbWU9c3BfbXRmJmFjdGlvbj1jbGlja1JlZGlyZWN0JmRvTm90TG9nQ2xpY2s9dHJ1ZQ==}{Amazon - \$59 Unzano Webcam $100^{\circ}$ FOV}.
\item 
\href{https://www.amazon.com/JIFFY-Upgrade-Microphones-Recording-Compatible/dp/B07CMG3ZN4/ref=sr_1_2_sspa?dchild=1&keywords=h264+webcam&qid=1597071160&sr=8-2-spons&psc=1&spLa=ZW5jcnlwdGVkUXVhbGlmaWVyPUExRVNTTjJZRURLNFE3JmVuY3J5cHRlZElkPUEwMjUzMDY0VzI3Nkw0RlVaQzg4JmVuY3J5cHRlZEFkSWQ9QTA1MzEzMjYxSEFLOTlPS05WWUNWJndpZGdldE5hbWU9c3BfYXRmJmFjdGlvbj1jbGlja1JlZGlyZWN0JmRvTm90TG9nQ2xpY2s9dHJ1ZQ==}{Amazon - \$55 JIFFY HD Webcam - }
\item
\href{https://www.amazon.com/TedGem-Streaming-Microphone-Widescreen-Conferencing/dp/B07R3KKBPD/ref=sr_1_4?dchild=1&keywords=h264+webcam&qid=1597071160&sr=8-4}{\$44 Webcam - $90^{\circ}$ FOV}
\end{itemize}

\end{gram}

\section{Desktop Tripod}
\label{sec:equipment::tripod}

\subsection{Mama-Win}
\label{sec:equipment::tripod::mamawin}

\begin{gram}
\label{grm:equipment::tripod::mamawin::main}

\textbf{Overview}

This is a light weight mini webcam tripod for smartphone and Logitech webcam.
%
\begin{itemize}
\item
Mini tripod with adjustable-height metal legs and rubber feet

\item
Compatible with small digital cameras (not DSLRs), GoPro devices, and smartphone adapters 

\item
Mini ball head for 360-degree rotation and 90-degree tilt

\item
Provides Support And Stability For Cameras, Webcams, Imaging Devices, etc

\end{itemize}



\textbf{Expected price}

\$13

\textbf{Where to buy}

\href{https://www.amazon.com/Lightweight-Webcam-Tripod-Logitech-Camera/dp/B076SHC6RN/ref=sr_1_1_sspa?crid=2T6CQ3HNRR1XR&keywords=logitech+c920&qid=1582900721&s=electronics&sprefix=logitech+c,electronics,172&sr=1-1-spons&psc=1&spLa=ZW5jcnlwdGVkUXVhbGlmaWVyPUE1VjVUUFpKTU83QUkmZW5jcnlwdGVkSWQ9QTA1NTk1OTVLT1IyTzdRRFVEWkImZW5jcnlwdGVkQWRJZD1BMDEyNzk2NzEyTDVSOEdSQ1QxTEgmd2lkZ2V0TmFtZT1zcF9hdGYmYWN0aW9uPWNsaWNrUmVkaXJlY3QmZG9Ob3RMb2dDbGljaz10cnVl}{Amazon}

\end{gram}


\section{Accessories}
\label{sec:equipment::accessories}

\subsection{USB 2.0 Extension Cable}
\label{sec:equipment::accessories::usbextend}

\begin{gram}
\label{grm:equipment::accessories::usbextend}
\textbf{More Details}

Full details available on \href{https://www.amazon.com/AmazonBasics-Extension-Cable-Male-Female/dp/B00NH11PEY/ref=sr_1_3?crid=37GCZPQHYO54W&keywords=usb+extension+cable&qid=1582900847&s=electronics&sprefix=usb+ext,electronics,164&sr=1-3}{Amazon}

\begin{itemize}
\item USB 2.0
\item A-Male to A-Female Adapter Cord
\item  One 6.5 or 9.8-foot-long (2 or 3 meters) high-speed extension cable
\item Extends your USB connection to your computer with USB computer peripherals
\item 
Constructed with corrosion-resistant, gold-plated connectors
\item Features shielding that provides protection against noise from electromagnetic and radio-frequency signals
\item Typically, the Male A connector plugs into your computer and the Female A connects to the cable you need extended. 

\end{itemize}

\textbf{Expected Price}

\$ 5-10

\textbf{Where to buy}

\begin{itemize}
\item 
6.5 feet
\href{https://www.amazon.com/AmazonBasics-Extension-Cable-Male-Female/dp/B00NH136G}{Amazon}

\item
9.8 feet

\href{https://www.amazon.com/AmazonBasics-Extension-Cable-Male-Female/dp/B00NH11PEY/ref=sr_1_3?crid=37GCZPQHYO54W&keywords=usb+extension+cable&qid=1582900847&s=electronics&sprefix=usb+ext,electronics,164&sr=1-3}{Amazon}
\end{itemize}
\end{gram}

\begin{gram}[USB 3.0 Adapters]
Some of the equipment such as Wacom displays need two connections with
your computer/laptop 1) a display port or HDMI connection 2) a USB 2.0
connection.
%
Depending on your computer, you might need an adapter, e.g., one that bridges the two above with a USB 3.0.
%
Here are several adapters that we have tried and tested.

\begin{itemize}

\item For Lenovo t480s running linux:
\href
{https://www.lenovo.com/us/en/accessories-and-monitors/travelers/CABLE-BO-USB-C-3-in-1-Hub-ROW/p/GX90T33021}
{Lenove USB 3-in-1}
.
This adapteris listed for \$50.
%
It may be cheaper
\href
{https://www.amazon.com/gp/product/B07NPDR49R/ref=ppx_yo_dt_b_asin_title_o04_s00?ie=UTF8&psc=1}
{on Amazon}.

\item For Macs:
\href{https://www.apple.com/shop/product/MUF82AM/A/usb-c-digital-av-multiport-adapter
}
{Apple USB-C Digital AV Multiport Adapter}.
This adapter is \$69 and is also available 
\href{https://www.amazon.com/gp/product/B07WF96FY5/ref=ppx_yo_dt_b_asin_title_o07_s00?ie=UTF8&psc=1}
{on Amazon}
\end{itemize}
\end{gram}
